Query Optimization for Dynamic Imputation

### 2017-03-01 paper/conclusion.tex

\textbf{Imputation confidence:} Obtaining a confidence measure for query results
produced when missing values are imputed with a machine learning model is
another possible improvement to the system. In most cases, the data imputed
is unlikely to follow a standard distribution, but iterative approaches such as cross-validation\cite{kohavi1995study}
can give confidence intervals.
In contrast to standard confidence calculations, there is the added complexity
of imputation taking place at various points in the plan, so the composition of results
through standard query operations needs to be taken into account when computing confidence intervals.

>>>>

\textbf{Imputation confidence:} Obtaining confidence measures for query results
produced when missing values are imputed with a machine learning model is
another possible improvement to the system. These measures could be obtained in general
using resampling methods like cross-validation and bootstrapping\cite{kohavi1995study}.
In contrast to standard confidence calculations, there is the added complexity that
imputation takes place at various points in the plan, so the composition of results
through standard query operations needs to be taken into account when computing confidence intervals.
Finally, multiple imputation could be considered explicitly and confidence measures like variances could
similarly propagate through the query plan.
